**OptiClust: Improved method for assigning amplicon-based sequence data to operational taxonomic units**

### 2016-12-23 submission/Westcott_OptiClust_mSphere_2016.Rmd
Embed images into manuscript file for initial submission

---
title: "**OptiClust: Improved method for assigning amplicon-based sequence data to operational taxonomic units**"
bibliography: references.bib
output:
  pdf_document:
    includes:
      in_header: header.tex
csl: msphere.csl
fontsize: 11pt
geometry: margin=1.0in
---

@@

**Running title:** OptiClust: Optimized Clustering

\begin{center}
\vspace{25mm}
Sarah L. Westcott and Patrick D. Schloss${^\dagger}$

@@

## Acknowledgements
This work was supported through funding from the National Institutes of Health to PDS (). SLW designed, implemented, and evaluated the algorithm. PDS designed and evaluated the algorithm. Both authors wrote and edited the manuscript.

@@

```{r results='asis', echo=FALSE, warning=FALSE, eval=TRUE}
library('xtable')

options(xtable.sanitize.text.function=identity)

@@

dataset_ref <- paste0(dataset, ' (', reference, ')')

@@

colnames(data_table) <- c("Dataset (Ref.)",
													"\\bigcell{c}{Read \\\\ Length }",
													"\\bigcell{c}{Samples \\\\ (N) }",
													"\\bigcell{c}{Total \\\\ Seqs. (N)}",
													"\\bigcell{c}{Unique \\\\ Seqs. (N) }")

colnames(data_table) <- paste0("\\textbf{", colnames(data_table), "}")

composite <- xtable(data_table, label="")

align(composite) <- "llcccc"

print(composite,
		include.rownames=FALSE,
		include.colnames=TRUE,
		hline.after = c(-1,0, nrow(composite)),
		comment=FALSE,
		table.placement="!ht"
		)
```

@@

## Figures

@@

@@

>>>>

---
title: "**OptiClust: Improved method for assigning amplicon-based sequence data to operational taxonomic units**"
bibliography: references.bib
output:
  pdf_document:
    includes:
      in_header: header.tex
    fig_caption: false
csl: msphere.csl
fontsize: 11pt
geometry: margin=1.0in
---

@@

\begin{center}

**Running title:** OptiClust: Optimized Clustering
\vspace{25mm}
Sarah L. Westcott and Patrick D. Schloss${^\dagger}$

@@

## Acknowledgements
This work was supported through funding from the National Institutes of Health to PDS (P30DK034933). SLW designed, implemented, and evaluated the algorithm. PDS designed and evaluated the algorithm. Both authors wrote and edited the manuscript.

@@

```{r results='asis', echo=FALSE, warning=FALSE, eval=TRUE}

@@

dataset_ref <- paste0(dataset, ' ', reference)

@@

colnames(data_table) <- c("**Dataset (Ref.)**",
													"**Read Length**",
													"**Samples**",
													"**Total Seqs.**",
													"**Unique Seqs.**")

kable(data_table, row.names=F, align="lcccc")

@@

\includegraphics[width=6.0in]{../results/figures/performance.png}

@@

\includegraphics[width=3.5in]{../results/figures/speed_memory.png}

@@

\includegraphics[width=3.5in]{../results/figures/split_mcc.png}
